---
title: "sc bench benchmark"
author: ""
format: 
  dashboard: 
    logo: "https://www.sydney.edu.au/etc.clientlibs/corporate-commons/clientlibs/foundation/resources/corporate-frontend/assets/img/favicon/favicon-16x16.png"
    theme: 
      - slate
      - custom.scss
---

```{r}
#| label: load-packages
#| echo: false
#| include: false

library(tidyverse)
library(DT)
library(data.table)
library(bslib)
library(bsicons)
```

```{r}
#| label: load-data
#| message: false


data <- read.csv("data/data.csv")

```

# Paper

## Column {width="100%"}

### Row {.tabset}

#### Category

###### Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Valuebox 1"
list(
  icon = "book",
  color = "warning",
  value = 3
)
```

```{r}
#| content: valuebox
#| title: "Valuebox 2"
list(
  icon = "book",
  color = "info",
  value = 4
)
```

```{r}
#| content: valuebox
#| title: "Valuebox 3"
list(
  icon = "trash",
  color = "danger",
  value = 10
)
```

::: {.valuebox icon="arrow-repeat" color="vb-warning"}
In Progress

3 4
:::


###### Row {height="80%"}

```{r}
#| title: Pure or New method


```

Placeholder for Pure and method

#### Survey Analysis

##### Row {height="15%"}

Placeholder text for top row (Selection)

##### Row {height="85%"}

::: {.card title="card Title"}
This is a card
:::

```{r}
#| title: card title

```

# Data overview

## Column {width="100%"}

```{r}
data.table(data)
```

# Evaluation Summary

## Row {.tabset}

### Journal

#### Column {width="50%"}

```{r}
#| title: Pure Benchmark
```

#### Column {width="50%"}

```{r}
#| title: New Method
```

### Publication Year

#### Column {width="50%"}

```{r}
#| title: Pure Benchmark

```
#### Column {width="50%"}

```{r}
#| title: New Method
```

### Category Frequency

#### Column {width="50%"}

```{r}
#| title: Pure Benchmark
```

#### Column {width="50%"}

```{r}
#| title: New Method
```


### Statistics


```{r}
#| title: List of statistics
```
Statistics

# General Information

{{<include information/index.qml}}